Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2023-09-18 Paper/Supplementary.tex
Adding variable names

$\mysp(\samplesymt)$  & Sp\_n & dB re 1 $\textrm{m}^2$ & Point scattering strength.\\
$\sv$  & & dB re 1 $\textrm{m}^{-1}$ & Volume backscattering strength.\\
$\sv(\freqsym)$ & & dB re 1 $\textrm{m}^{-1}$ & Volume backscattering strength at frequency $\freqsym$.\\
$\sv(\samplesymt)$ & Sv\_n & dB re 1 $\textrm{m}^{-1}$ & Volume backscattering strength at sample index $\samplesymt$.\\

@@

$\hannw$ & & 1 & The Hann window function.\\
$\hannw(\genidxsym)$ & w\_i & 1 & The Hann window function for index i, defined by $w(i) = 0.5(1+\cos (2\pi i /N_w)), -N_w/2 \leq i \leq N_w/2$.\\
$\hannwnorm(\genidxsym)$ & w\_tilde\_i & 1 & Normalised Hann window.\\

@@

$\ymfautof(\samplesymf)$ & Y\_mf\_auto\_m & 1 & Discrete Fourier transform (DFT) of the autocorrelation function for the matched filter.\\
$\ymfautoredf(\samplesymf)$ & Y\_mf\_auto\_m\_red & 1 & DFT of the reduced autocorrelation function for the matched filter.\\
$\ypctargetf(\samplesymf)$ & Y\_pc\_t\_m & V & DFT of the pulse compressed signal from a single target.\\
$\ypctargetnormf(\samplesymf)$ & Y\_tilde\_pc\_t\_m & Vm & DFT of the pulse compressed signal from a single target 
normalized by the DFT of the reduced autocorrelation function for the matched filter.\\
$\ypcvolumef(\samplesymf)$ & Y\_pc\_v\_m & Vm & DFT of the pulse compressed signal from a volume. Compensated for spreading loss.\\
$\ypcvolumenormf(\samplesymf)$ & \code{Y\_tilde\_pc\_v\_m} & V & DFT of the pulse compressed signal from a single volume normalized by the DFT of the reduced autocorrelation function for the matched filter.  Compensated for spreading loss.\\

$\ymf(\samplesymt)$ & & 1 & Matched filter. Signal used for pulse compression.\\
$\ymfauto(\samplesymt)$ & & 1 & Autocorrelation function for the matched filter.\\
$\ymfautored(\samplesymt)$ & \code{y_mf_auto_red_n} & 1 & Reduced autocorrelation function for the matched filter.\\

$\ypc(\samplesymt)$ & & V & Pulse compressed signal averaged over all transducer sectors.\\
$\ypc(\samplesymt, \channelsym) $ & & V & Pulse compressed signal from channel $\channelsym$.\\
$y_{\textrm{pc,aft}}(\samplesymt)$ & & V & Pulse compressed signal from the aft transducer half.\\
$y_{\textrm{pc,fore}}(\samplesymt)$ & & V & Pulse compressed signal from the forward transducer half.\\
$y_{\textrm{pc,port}}(\samplesymt)$ & & V & Pulse compressed signal from the port transducer half.\\
$\ypcspread(\samplesymt)$ & & Vm & Pulse compressed signal compensated for spherical spreading.\\
$y_{\textrm{pc,star}}(\samplesymt)$ & & V & Pulse compressed signal from the starboard transducer half.\\
$\ypctarget(\samplesymt)$ & & V & Pulse compressed signal from a single target.\\

$\yrx(\samplesymt,\channelsym)$ & & V & Received digitised, bandpass filtered, decimated complex signal after the final filter stage, $\yrx(\samplesymt,\channelsym) = \yrx(\samplesymt,\channelsym,\nstages)$.\\
$\yrx(\samplesymt,\channelsym,\stagesym)$ & & V & Received digitised, bandpass filtered, decimated complex signal.\\
$\yrxa(\timesym)$ & & Pa & Analogue acoustic signal received by the transducer.\\
% $\yrxa(\timesym,\channelsym)$ & & Pa & Analogue acoustic signal received by each transducer sector $\channelsym$.\\
$\yrxe(\timesym,\channelsym)$ & & V & Analogue electric signal received by each transceiver channel $\channelsym$.\\

@@

$\ytx(\samplesymt)$ & & V & Ideal transmitted signal generated from transmit signal properties.\\
$\ytxnorm(\samplesymt)$ & & 1 & Ideal normalized transmitted signal generated from transmit signal properties.\\
$\ytxnorm(\samplesymt,\stagesym)$ & & 1 & Ideal normalized transmitted signal generated from transmit signal properties after application of filter stage $\stagesym$.\\

@@

$y_\along(\samplesymt)$ & & rad & Electrical angle along the minor axis of the transducer (alongship when ship-mounted).\\
$y_\athw(\samplesymt)$ & & rad & Electrical angle along the major axis of the transducer (athwartship when ship-mounted).\\

$\zrxe$ & & $\Omega$ & Receiver electric impedance.\\
$\ztde$ & & $\Omega$ & Transducer sector electric impedance.\\

$\absorp(\freqsym)$  & & dB $\textrm{m}^{-1}$ & Absorption coefficient at frequency $f$.\\
% $\absorp(\samplesymf)$ & & dB $\textrm{m}^{-1}$ & Absorption coefficient at frequency index $m$\\
$\anglefalong$ & & 1 & Conversion factor between phase difference in signals from the fore and aft transducer halves and the physical arrival angle of an echo.\\
$\anglefathw$ & & 1 & Conversion factor between phase difference in signals from the port and starboard transducer halves and the physical arrival angle of an echo.\\
$\along$ & & rad & Angle coordinates along the minor axis of the transducer (alongship when ship-mounted).\\
% $\along(\samplesymt)$ & & rad & Angle of arrival of target echo along the minor axis of the transducer (alongship when ship-mounted).\\
$\wlen$ & & m &  Acoustic wavelength.\\
$\wlen_\samplesymf$ & & m & Acoustic wavelength at frequency index $m$\\
$\sigmabs$ & & $\textrm{m}^2$ & Backscattering cross-section.\\
$\tnom$ & & s & Nominal transmit pulse duration.\\
$\teff$ & & s & Effective transmit pulse duration.\\
$\athw$ & & rad & Angle coordinates along the major axis of the transducer (athwartship when ship-mounted).\\
% $\athw(\samplesymt)$ & & rad & Angle of arrival of target echo along the major axis of the transducer (athwartship when ship-mounted).\\
$\eqang(\freqsym)$ & & sr & Two-way equivalent beam angle at frequency $\freqsym$.\\
\end{longtable}

>>>>

$\mysp(\samplesymt)$  & \code{Sp_n} & dB re 1 $\textrm{m}^2$ & Point scattering strength.\\
$\sv$  & & dB re 1 $\textrm{m}^{-1}$ & Volume backscattering strength.\\
$\sv(\freqsym)$ & & dB re 1 $\textrm{m}^{-1}$ & Volume backscattering strength at frequency $\freqsym$.\\
$\sv(\samplesymt)$ & \code{Sv_n} & dB re 1 $\textrm{m}^{-1}$ & Volume backscattering strength at sample index $\samplesymt$.\\

@@

$\hannw$ & & 1 & The Hann window function.\\
$\hannw(\genidxsym)$ & \code{w_i} & 1 & The Hann window function for index i, defined by $w(i) = 0.5(1+\cos (2\pi i /N_w)), -N_w/2 \leq i \leq N_w/2$.\\
$\hannwnorm(\genidxsym)$ & \code{w_tilde_i} & 1 & Normalised Hann window.\\

@@

$\ymfautof(\samplesymf)$ & \code{Y_mf_auto_m} & 1 & Discrete Fourier transform (DFT) of the autocorrelation function for the matched filter.\\
$\ymfautoredf(\samplesymf)$ & \code{Y_mf_auto_m_red} & 1 & DFT of the reduced autocorrelation function for the matched filter.\\
$\ypctargetf(\samplesymf)$ & \code{Y_pc_t_m} & V & DFT of the pulse compressed signal from a single target.\\
$\ypctargetnormf(\samplesymf)$ & \code{Y_tilde_pc_t_m} & Vm & DFT of the pulse compressed signal from a single target 
normalized by the DFT of the reduced autocorrelation function for the matched filter.\\
$\ypcvolumef(\samplesymf)$ & \code{Y_pc_v_m} & Vm & DFT of the pulse compressed signal from a volume. Compensated for spreading loss.\\
$\ypcvolumenormf(\samplesymf)$ & \code{Y_tilde_pc_v_m} & V & DFT of the pulse compressed signal from a single volume normalized by the DFT of the reduced autocorrelation function for the matched filter.  Compensated for spreading loss.\\

$\ymf(\samplesymt)$ & \code{y_mf_n} & 1 & Matched filter. Signal used for pulse compression.\\
$\ymfauto(\samplesymt)$ & \code{y_mf_auto_n} & 1 & Autocorrelation function for the matched filter.\\
$\ymfautored(\samplesymt)$ & \code{y_mf_auto_red_n} & 1 & Reduced autocorrelation function for the matched filter.\\

$\ypc(\samplesymt)$ & \code{y_pc_n} & V & Pulse compressed signal averaged over all transducer sectors.\\
$\ypc(\samplesymt, \channelsym) $ & \code{y_pc_nu} & V & Pulse compressed signal from channel $\channelsym$.\\
$y_{\textrm{pc,aft}}(\samplesymt)$ & \code{y_pc_aft_n} & V & Pulse compressed signal from the aft transducer half.\\
$y_{\textrm{pc,fore}}(\samplesymt)$ & \code{y_pc_fore_n} & V & Pulse compressed signal from the forward transducer half.\\
$y_{\textrm{pc,port}}(\samplesymt)$ & \code{y_pc_port_n} & V & Pulse compressed signal from the port transducer half.\\
$\ypcspread(\samplesymt)$ & \code{y_pc_s_n} & Vm & Pulse compressed signal compensated for spherical spreading.\\
$y_{\textrm{pc,star}}(\samplesymt)$ & \code{y_pc_star_n} & V & Pulse compressed signal from the starboard transducer half.\\
$\ypctarget(\samplesymt)$ & \code{y_pc_t_n} & V & Pulse compressed signal from a single target.\\

$\yrx(\samplesymt,\channelsym)$ & \code{y_rx_nu} & V & Received digitised, bandpass filtered, decimated complex signal after the final filter stage, $\yrx(\samplesymt,\channelsym) = \yrx(\samplesymt,\channelsym,\nstages)$.\\
$\yrx(\samplesymt,\channelsym,\stagesym)$ & & V & Received digitised, bandpass filtered, decimated complex signal.\\
$\yrxa(\timesym)$ & & Pa & Analogue acoustic signal received by the transducer.\\
% $\yrxa(\timesym,\channelsym)$ & & Pa & Analogue acoustic signal received by each transducer sector $\channelsym$.\\
$\yrxe(\timesym,\channelsym)$ & & V & Analogue electric signal received by each transceiver channel $\channelsym$.\\

@@

$\ytx(\samplesymt)$ & \code{y_tx_n} & V & Ideal transmitted signal generated from transmit signal properties.\\
$\ytxnorm(\samplesymt)$ & \code{y_tilde_tx_n} & 1 & Ideal normalized transmitted signal generated from transmit signal properties.\\
$\ytxnorm(\samplesymt,\stagesym)$ & \code{y_tilde_tx_nv} & 1 & Ideal normalized transmitted signal generated from transmit signal properties after application of filter stage $\stagesym$.\\

@@

$y_\along(\samplesymt)$ & \code{y_theta_n} & rad & Electrical angle along the minor axis of the transducer (alongship when ship-mounted).\\
$y_\athw(\samplesymt)$ & \code{y_phi_n} & rad & Electrical angle along the major axis of the transducer (athwartship when ship-mounted).\\

$\zrxe$ & \code{z_rx_e} & $\Omega$ & Receiver electric impedance.\\
$\ztde$ & \code{z_td_e} & $\Omega$ & Transducer sector electric impedance.\\

$\absorp(\freqsym)$  & \code{alpha_m} & dB $\textrm{m}^{-1}$ & Absorption coefficient at frequency $f$.\\
% $\absorp(\samplesymf)$ & & dB $\textrm{m}^{-1}$ & Absorption coefficient at frequency index $m$\\
$\anglefalong$ & \code{gamma_theta} & 1 & Conversion factor between phase difference in signals from the fore and aft transducer halves and the physical arrival angle of an echo.\\
$\anglefathw$ & \code{gamma_phi} & 1 & Conversion factor between phase difference in signals from the port and starboard transducer halves and the physical arrival angle of an echo.\\
$\along$ & \code{theta_n} & rad & Angle coordinates along the minor axis of the transducer (alongship when ship-mounted).\\
% $\along(\samplesymt)$ & & rad & Angle of arrival of target echo along the minor axis of the transducer (alongship when ship-mounted).\\
$\wlen$ & & m &  Acoustic wavelength.\\
$\wlen_\samplesymf$ & \code{lambda_m} & m & Acoustic wavelength at frequency index $m$\\
$\sigmabs$ & & $\textrm{m}^2$ & Backscattering cross-section.\\
$\tnom$ & \code{tau} & s & Nominal transmit pulse duration.\\
$\teff$ & \code{tau_eff} & s & Effective transmit pulse duration.\\
$\athw$ & \code{phi} & rad & Angle coordinates along the major axis of the transducer (athwartship when ship-mounted).\\
% $\athw(\samplesymt)$ & & rad & Angle of arrival of target echo along the major axis of the transducer (athwartship when ship-mounted).\\
$\eqang(\freqsym)$ & \code{psi_m} & sr & Two-way equivalent beam angle at frequency $\freqsym$.\\
\end{longtable}
